Detecting Facial Expressions in Professional Tennis Matches

### 2017-03-29 Report06-12.Rmd
Changed Table Formats

#csv files:
ALLmetaIMG<-read_csv("ALLmetaIMG.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
FaceAttributes<-read_csv("TableCSVs/FaceAttributes.csv")
SolutionSpecs<-read_csv("TableCSVs/SolutionSpecifications.csv")

@@

    faceData <- ALLmetaIMGFaces %>% filter(file == i)

@@

#Factor Names 
ALLmetaIMG$graphic<-factor(ALLmetaIMG$graphic, levels = 0:1, labels = c("Live image", "Graphic"))
ALLmetaIMG$person<-factor(ALLmetaIMG$person, levels = 0:1, labels = c("No Person", "Person"))
ALLmetaIMG$situation<-factor(ALLmetaIMG$situation, levels = 0:5, labels = c("Court in play", "Court player close-up", "Court close-up not player", "Crowd", "Off court close up of player", "Transition"))
ALLmetaIMG$bg<-factor(ALLmetaIMG$bg, levels = 0:3, labels = c("Crowd", "Court", "Logo wall", "Not applicable"))
ALLmetaIMG$shotangle<-factor(ALLmetaIMG$shotangle, levels = 0:2, labels = c("Player Shoulder Height", "Birds Eye", "Upward Angle"))

ALLmetaIMG$detect<-factor(ALLmetaIMG$detect, levels = 0:2, labels = c("Player", "Other staff on court", "Fan"))
ALLmetaIMG$obscured<-factor(ALLmetaIMG$obscured, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$lighting<-factor(ALLmetaIMG$lighting, levels = 1:2, labels = c("Shaded", "Partially shaded"))
ALLmetaIMG$headangle<-factor(ALLmetaIMG$headangle, levels = 0:3, labels = c("Front on", "Back of head", "Profile", "Other"))
ALLmetaIMG$glasses<-factor(ALLmetaIMG$glasses, levels = 0:1, labels = c("No", "Yes"))
ALLmetaIMG$visorhat<-factor(ALLmetaIMG$visorhat, levels = 0:1, labels = c("No", "Yes"))

ALLmetaIMG$headangle <- as.character(ALLmetaIMG$headangle)
ALLmetaIMG$headangle[ALLmetaIMG$headangle == "Back of head"] <- "Other"
ALLmetaIMG$headangle <- as.factor(ALLmetaIMG$headangle)

ALLmetaIMGPlayers<- ALLmetaIMG %>% filter(detect=="Player")

# change this to facesVenn with binary information
ALLmetaIMGFaces<-ALLmetaIMG%>%
  filter(matchesManual) %>% 
  dplyr::select(-ID, -facecounter)%>%
  mutate(fileID = as.numeric(factor(file))) %>%
  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))

@@

```{r Trial-Image, fig.cap = "Initial Image Used For Testing\\label{Trial-Image}", message=TRUE, warning=TRUE}
imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
overlayGgplot(imagesList0, ALLmetaIMGFaces, matchBox = FALSE)
```

@@

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
knitr::kable(SceneAttributes, format = "markdown", longtable=TRUE, booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
```

@@

```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis',}
knitr::kable(SolutionSpecs, format = "markdown", longtable=TRUE, booktabs = TRUE, caption="")
```

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image. The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "markdown", longtable=TRUE, booktabs = TRUE)
```

@@

Using the data set^[ALLmetaIMG] of the combined API and manual results, we were able to compare the performance of the software.
Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(Face-Bounding-Box-Data).

@@

GlmModelCreation <- function(model, data = ALLmetaIMGFaces) {
  glmFits <- data %>% 
  split(.$FaceKey) %>% 
  map_df(~ hitmiss(.)) %>% 
  split(.$type) %>% 
  map(~ glm(model, data = dplyr::select(., -type, -file, -boxID), binomial(link = "logit")))
}

@@

```{r Face-Bounding-Box-Data, results='hide', fig.cap = "\\label{Face-Bounding-Box-Data} Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft."}
ggplot(ALLmetaIMG, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE) + labs(caption="")
```

@@

```{r Face-Bounding-Box-UpSet, fig.cap = "\\label{Face-Bounding-Box-Upset} Face Bounding Boxes Per Software Combination. The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software. The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations. The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API."}
createUpSet(ALLmetaIMGFaces)
```

```{r I3, results=TRUE, fig.cap = "\\label{fig:I3} There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face."}
imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
overlayGgplot(imagesList3, ALLmetaIMGFaces, matchBox = FALSE)
```

@@

```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}
NoManual<-ALLmetaIMG %>% filter(ALLmetaIMG$type!="Manual")
NoManual<-NoManual %>% droplevels(NoManual$type) 
Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
ct<-CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
print(ct)
```

@@

```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- ALLmetaIMG %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:10,]
knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="", format = "markdown")
```

@@

```{r Typical-Best-Recognised, results=FALSE, fig.cap = "\\label{fig:Typical-Best-Recognised}"}
imagesList1<-as.list("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png")
overlayGgplot(imagesList1, ALLmetaIMG, matchBox = FALSE)
```

@@

GoogleNoMatch <- ALLmetaIMG %>%
  filter(type=="Google") %>%
  filter(matchesManual==FALSE) %>%
  group_by(person, situation, bg, shotangle) %>% dplyr::summarise(count=n())

@@

GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
knitr::kable(GoogleNoMatch[1:10,], caption="", longtable=TRUE, format = "markdown")

@@

FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
knitr::kable(FaceCharacteristics, caption="", longtable=TRUE, format = "markdown")
```

@@

```{r Glasses, fig.cap = "\\label{tab:Glasses} This table shows the amount of faces recognised by google wearing glasses. The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally."}
GlassesGoogle <- ALLmetaIMGFaces %>% filter(type=="Google") %>%
filter(matchesManual==TRUE)
pander(table(GlassesGoogle$glasses))
```

@@

```{r Accuracy}
Accuracy<-with(ALLmetaIMG, table(ALLmetaIMG$matchesManual, ALLmetaIMG$type))
knitr::kable(Accuracy, caption="", longtable=TRUE, format = "markdown")
# make this a proportional table, would this be necessary if we have the UpSetR
```

@@

```{r Google-Characteristics-Table, fig.cap = "\\label{tab:Google-Characteristics-Table}"}
GoogleCharacteristics <- ALLmetaIMG %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
GoogleCharacteristics<-arrange(GoogleCharacteristics, desc(count))

knitr::kable(GoogleCharacteristics, format = "markdown", longtable=TRUE, booktabs = TRUE, caption="")
```

>>>>

#csv files:
ALLmetaIMGnamed<-read_csv("ALLmetaIMGnamed.csv", col_types = cols(type = col_factor(levels = c("Manual", "Animetrics", "Google", "Microsoft", "Skybiometry"))))
SceneAttributes<-read_csv("TableCSVs/SceneAttributes.csv")
FaceAttributes<-read_csv("TableCSVs/FaceAttributes.csv")
SolutionSpecs<-read_csv("TableCSVs/SolutionSpecifications.csv")

@@

    faceData <- ALLmetaIMGnamedFaces %>% filter(file == i)

@@

ALLmetaIMGPlayers<- ALLmetaIMGnamed %>% filter(detect=="Player")

# change this to facesVenn with binary information
ALLmetaIMGnamedFaces<-ALLmetaIMGnamed%>%
  #filter(matchesManual) %>% 
  dplyr::select(-ID, -facecounter)%>%
  mutate(fileID = as.numeric(factor(file))) %>%
  mutate(FaceKey=paste(fileID, boxID, sep="-")) %>%
  mutate(FaceID=paste(fileID, boxID, substring(type, 1,2), sep="-"))

@@

```{r Trial-Image, fig.cap = "Initial Image Used For Testing\\label{Trial-Image}", message=TRUE, warning=TRUE}
imagesList0<-as.list("2016_HSA_R01_BTomic_AUS_vs_DIstomin_UZB_MS157_clip.0013.png")
overlayGgplot(imagesList0, ALLmetaIMGnamedFaces, matchBox = FALSE)
```

@@

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
knitr::kable(SceneAttributes, format = "latex", longtable=TRUE, booktabs = TRUE, caption = "Attributes of a Scene of an image. The most appropriate option from the list was selected for each attribute.")
```

@@

```{r Solution-Specifications-Table, fig.cap = "\\label{tab:Solution-Specifications-Table}", results='asis'}
knitr::kable(SolutionSpecs, format = "latex", longtable=TRUE, booktabs = TRUE, caption="")
```

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "Attributes of an individual face within an image. The most appropriate option from the list was selected for each attribute.\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "latex", longtable=TRUE, booktabs = TRUE)
```

@@

Using the data set^[ALLmetaIMGnamed] of the combined API and manual results, we were able to compare the performance of the software.
Firstly, we considered how many individual faces the software were able to detect in Figure \@ref(Face-Bounding-Box-Data).

@@

GlmModelCreation <- function(model, data = ALLmetaIMGnamedFaces) {
  glmFits <- data %>% 
  split(.$FaceKey) %>% 
  map_df(~ hitmiss(.)) %>% 
  split(.$type) %>% 
  map(~ glm(model, data = dplyr::select(., -type, -file, -boxID), binomial(link = "logit")))
}

@@

```{r Face-Bounding-Box-Data, results='hide', fig.cap = "\\label{Face-Bounding-Box-Data} Face Bounding Boxes Per Software: The bar chart above shows the number of Bounding Boxes produced by each software, comparing the height of the bars indicates that Google's Facial Recognition software recognized almost 1000 more faces than the next best software, Microsoft."}
ggplot(ALLmetaIMGnamed, aes(x = type, fill=type)) + geom_bar(position="dodge") +xlab("Facial Recognition Softwares")+scale_x_discrete(limits=c("Manual","Google","Microsoft","Skybiometry","Animetrics")) +ylab("Number of Potential Faces") + guides(fill=FALSE) + labs(caption="")
```

@@

```{r Face-Bounding-Box-UpSet, fig.cap = "\\label{Face-Bounding-Box-Upset} Face Bounding Boxes Per Software Combination. The Bar Chart shows the Face Bounding Boxes that were recognised by multiple software. The largest group with 809 faces is Face Bounding Boxes only found by Manual annotations. The following group was Boxes representing the same faces being recognized by both Manual annotations and the Google API."}
createUpSet(ALLmetaIMGnamedFaces)
```

```{r I3, results=TRUE, fig.cap = "\\label{fig:I3} There is an unusual classification where just right of the center, the smaller box actually captures a fist, not a face."}
imagesList3<-as.list("2016_SC2_R01_ATomljanovic_AUS_vs_KBondarenko_UKR_WS1112_clip.0053.png") 
overlayGgplot(imagesList3, ALLmetaIMGnamedFaces, matchBox = FALSE)
```

@@

```{r Type-Matches-Manual, fig.cap = "\\label{tab:Type-Matches-Manual}"}
NoManual<-ALLmetaIMGnamed %>% filter(ALLmetaIMGnamed$type!="Manual")
NoManual<-NoManual %>% droplevels(NoManual$type) 
Accuracy<-with(NoManual, table(NoManual$matchesManual, NoManual$type))
ct<-CrossTable(Accuracy, prop.chisq = FALSE, cell.layout = TRUE, digits=4)
print(ct)
```

@@

```{r Image-Characteristics-Table, fig.cap = "\\label{tab:Image-Characteristics-Table}"}
ImageCharacteristics <- ALLmetaIMGnamed %>% filter(type=="Manual") %>% group_by(situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
ImageCharacteristics<-arrange(ImageCharacteristics, desc(count))
ImageCharacteristics<-ImageCharacteristics[1:10,]
knitr::kable(ImageCharacteristics, booktabs = TRUE, longtable=TRUE, caption="", format = "latex")
```

@@

```{r Typical-Best-Recognised, results=FALSE, fig.cap = "\\label{fig:Typical-Best-Recognised}"}
imagesList1<-as.list("2016_CT6_R01_JMillman_AUS_vs_DSchwartzman_ARG_MS159_clip.0013.png")
overlayGgplot(imagesList1, ALLmetaIMGnamed, matchBox = FALSE)
```

@@

GoogleNoMatch <- ALLmetaIMGnamed %>%
  filter(type=="Google") %>%
  filter(matchesManual==FALSE) %>%
  group_by(person, situation, bg, shotangle) %>% dplyr::summarise(count=n())

@@

GoogleNoMatch<-arrange(GoogleNoMatch, desc(count))
knitr::kable(GoogleNoMatch[1:10,], caption="", longtable=TRUE, format = "latex")

@@

FaceCharacteristics<-arrange(FaceCharacteristics, desc(count))
FaceCharacteristics<-as.tbl(FaceCharacteristics[1:10,])
knitr::kable(FaceCharacteristics, caption="", longtable=TRUE, format = "latex")
```

@@

```{r Glasses, fig.cap = "\\label{tab:Glasses} This table shows the amount of faces recognised by google wearing glasses. The strong disparity between the amount of faces with glasses to faces without them means that the occurrence of these attributes across the software must be considered proportionally."}
GlassesGoogle <- ALLmetaIMGnamedFaces %>% filter(type=="Google") %>%
filter(matchesManual==TRUE)
pander(table(GlassesGoogle$glasses))
```

@@

```{r Accuracy}
Accuracy<-with(ALLmetaIMGnamed, table(ALLmetaIMGnamed$matchesManual, ALLmetaIMGnamed$type))
knitr::kable(Accuracy, caption="", longtable=TRUE, format = "latex")
# make this a proportional table, would this be necessary if we have the UpSetR
```

@@

```{r Google-Characteristics-Table, fig.cap = "\\label{tab:Google-Characteristics-Table}"}
GoogleCharacteristics <- ALLmetaIMGnamed %>% filter(type=="Google") %>% filter(person=="Person") %>% filter(situation=="Court player close-up") %>% filter(bg=="Logo wall") %>% filter(detect=="Player") %>% group_by(person, situation, bg, shotangle, detect) %>% dplyr::summarise(count=n())
GoogleCharacteristics<-arrange(GoogleCharacteristics, desc(count))

knitr::kable(GoogleCharacteristics, format = "latex", longtable=TRUE, booktabs = TRUE, caption="")
```
